Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 robdml.tex
tex

\textbf{Adversarial Defense.}
%
To battle against the attacks, some early defense methods create a gradient
masking effect, namely making it hard for the attacker to find a good gradient,
but it gives a false sense of security~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} can be compromised by C\&W~\cite{cw}.
%
Ensemble of weak defenses is insufficient~\cite{ensembleweak}.
%
Defense can also be implemented as preprocessing~\cite{deflecting} the input
image, or a randomized process inside the network~\cite{self-ensemble}.
%
However, it is noted that various defense methods are still susceptible to
adaptive attack~\cite{adaptive}.
%
Among the proposed defense methods, adversarial training has been empirically
found effective~\cite{bilateral,advtrain-triplet,benchmarking}, and it
consistently retains adversarial robustness for the model.

>>>>

\textbf{Adversarial Defense.}
%
To battle against the attacks, some early defenses incur gradient masking
effect, but it gives a false sense of security~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} can be compromised~\cite{cw}.
%
Ensemble of weak defenses is not robust~\cite{ensembleweak}.
%
Other forms of defenses are also proposed, such as input
preprocessing~\cite{deflecting}, or a randomization inside the
network~\cite{self-ensemble}.
%
But various defense methods are still susceptible to adaptive
attack~\cite{adaptive}.
%
Of all defenses, adversarial training remains to be one of the most
effective method~\cite{bilateral,advtrain-triplet,benchmarking}, and it
consistently show promising empirical robustness,
although suffering from significant training time cost and a lower performance
on benign examples.
